\subsection*{Peer-reviewed journal articles}
Gaidai, R., \textbf{Goelz, C.}, Mora, K., Rudisch, J., Reuter, E.-M., Godde, B., Reinsberger, C., Voelcker-Rehage, C. \& Vieluf, S. Classification characteristics of fine motor experts based on electroencephalographic and force tracking data. \textit{Brain Research} \textbf{1792}, 148001 (2022)\symbfootnote{Shared first authorship between R. Gaidai and C. Goelz}\setcounter{footnote}{0}\footnote{Publication considered for thesis}\\
\\
\textbf{Goelz, C.}, Mora, K., Rudisch, J., Gaidai, R., Reuter, E.-M., Godde, B., Reinsberger, C., Voelcker-Rehage, C. \& Vieluf, S. Classification of visuomotor tasks based on electroencephalographic data depends on age-related differences in brain activity patterns. \textit{Neural Networks} \textbf{142}, 363--374 (2021)\footnotemark[1]\\
\\
\textbf{Goelz, C.}, Mora, K., Stroehlein, J., Haase, F., Dellnitz, M., Reinsberger, C. \& Vieluf, S. Electrophysiological signatures of dedifferentiation differ between fit and less fit older adults. \textit{Cognitive Neurodynamics} \textbf{15}, 1--13 (2021)\footnotemark[1]\\
\\
\textbf{Goelz, C.}, Reuter, E.-M., Fröhlich, S., Rudisch, J., Godde, B., Vieluf, S. \& Voelcker-Rehage, C. Classification of age groups and task conditions provides additional evidence for differences in electrophysiological correlates of inhibitory control across the lifespan. \textit{Brain Informatics} \textbf{10}, 11 (2023)\footnotemark[1]\\
\\
Gowik, J. K., \textbf{Goelz, C.}, Vieluf, S., van den Bongard, F. \& Reinsberger, C. Source connectivity patterns in the default mode network differ between elderly golf-novices and non-golfers. \textit{Scientific Reports} \textbf{13}, 6215 (2023)\\
\newpage
\noindent\textbf{Gölz, C.}, Voelcker-Rehage, C., Mora, K., Reuter, E.-M., Godde, B., Dellnitz, M., Reinsberger, C. \& Vieluf, S. Improved Neural Control of Movements Manifests in Expertise-Related Differences in Force Output and Brain Network Dynamics. \textit{Frontiers in Physiology} \textbf{9} (2018)\\
\\
Niess, A., Widmann, M., Gaidai, R., \textbf{Gölz, C.}, Schubert, I., Castillo, K., Sachs, J. P., Bizjak, D., Vollrath, S., Wimbauer, F., Vogel, A., Keller, K., Burgstahler, C., Quermann, A., Kerling, A., Schneider, G., Zacher, J., Diebold, K., Grummt, M., Beckendorf, C., Buitenhuis, J., Egger, F., Venhorst, a., Morath, O., Barsch, F., Mellwig, K.-P., Oesterschlink, J., Wüstenfeld, J., Predel, H.-G., Deibert, P., Friedmann-Bette, B., Mayer, F., Hirschmüller, A., Halle, M., Steinacker, J. M., Wolfarth, B., Meyer, T., Böttinger, E., Flechtner-Mors, M., Bloch, W., Haller, B., Roecker, K. \& Reinsberger, C. COVID-19 in German Competitive Sports: Protocol for a Prospective Multicenter Cohort Study (CoSmo-S). \textit{International Journal of Public Health} \textbf{67}, 1604414 (2022)\\
\\
Stroehlein, J. K., Vieluf, S., Zimmer, P., Schenk, A., Oberste, M., \textbf{Goelz, C.}, van den Bongard, F. \& Reinsberger, C. Learning to play golf for elderly people with subjective memory complaints: feasibility of a single-blinded randomized pilot trial. BMC Neurology \textbf{21}, 200 (2021)\\
\\
Strote, C., \textbf{Gölz, C.}, Stroehlein, J. K., Haase, F. K., Koester, D., Reinsberger, C. \& Vieluf, S. Effects of force level and task difficulty on force control performance in elderly people. \textit{Experimental Brain Research} \textbf{238}, 2179--2188 (2020)\\
\\
Ströhlein, J. K., Vieluf, S., van den Bongard, Franziska, \textbf{Gölz, C.} \& Reinsberger, C. Golf spielen gegen die Vergesslichkeit: Effekte des Erlernens der Sportart auf das Default Mode Netzwerk des Gehirns. \textit{B\&G Bewegungstherapie und Gesundheitssport} \textbf{36}, 65--72 (2020)\\
\\
Vieluf, S., Mora, K., \textbf{Gölz, C.}, Reuter, E.-M., Godde, B., Dellnitz, M., Reinsberger, C. \& Voelcker-Rehage, C. Age-and expertise-related differences of sensorimotor network dynamics during force control. \textit{Neuroscience} \textbf{388}, 203--213 (2018)\\

\subsection*{Contributions to Conferences}
\subsubsection*{Talks\footnote{First author was always the presenting author}}
Gaidai, R., \textbf{Gölz, C.}, Widmann, M., Niess, A. M. \& Reinsberger, C. \textit{Herausforderungen und Lösungen im Aufbau eines Datenbanksystems im Verbundprojekt „Covid-19 im Spitzensport - Eine multizentrische Kohortenstudie“ (CoSmo-S).} Sports Medicine and Health Summit. Hamburg, Germany, June 2023\\
\\
\textbf{Goelz, C.}, Gaidai, R., Mora, K., Rudisch, J., Reuter, E. M., Godde, B., Reinsberger, C., Voelcker-Rehage, C. \& Vieluf, S. \textit{Classification characteristics of fine motor experts based on electroencephalographic and force tracking data}. 54th Annual Conference of the German Society for Sport Psychology. Muenster, Germany, June 2022\\
\\
Ströhlein, J., \textbf{Gölz, C.}, Vieluf, S., van den Bongard, F. \& Reinsberger, C.\textit{ Funktionelle Netzwerkcharakteristika des Default Mode Netzwerks bei älteren Golf-Novizen.} Sports Medicine and Health Summit. Virtual Conference, Apr. 2021\\
\\
Vieluf, S., Reinsberger, C., \textbf{Gölz, C.} \& Voelcker-Rehage, C. \textit{Age- and expertise related differences of sensorimotor network dynamics during force control.} 23rd University Day of the German Society of Sport Science. Munich, Germany, Sept. 2017\\

\subsubsection*{Poster\footnotemark[2]}
Gaidai, R., \textbf{Gölz, C.}, Widmann, M., Niess, A. M. \& Reinsberger, C. \textit{Herausforderungen und Lösungen im Aufbau eines Datenbanksystems im Verbundprojekt „Covid-19 im Spitzensport - Eine multizentrische Kohortenstudie“ (CoSmo-S). Nachwuchsssymposium Deutsche Gesellschaft für Sportmedizin und Prävention.} Tuebingen, Germany, Sept. 2022\\
\\
\textbf{Goelz, C.}, Mora, K., Stroehlein, J., Reinsberger, C. \& Vieluf, S. \textit{Electrophysiological signatures of brain network dynamics in elderly.} 26th Annual Meeting of the Organization of Human Brain Mapping. Virtual Conference, June 2020\\
\\
Vieluf, S., Voelcker-Rehage, C., \textbf{Goelz, C.}, Mora, K. \& Reinsberger, C. \textit{Age- and expertise-related differences in force control manifest in variability.} 27th Annual Meeting of the Society of the Neural Control of Movements. Dublin, Ireland, May 2017
